Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-22 WRITEUP/ms.tex
comparison of gas and HST sizes

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the C06 lens model (converted to
our cosmology) over the {\it HST} $I$-band image.
We note that the source plane half-light radius varies substantially with
wavelength: $R_e$ $\sim$\,4kpc and $\sim$7\,kpc based on models over
$V$-band \citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces recent massive \SF.
% On the other hand, $I$-band traces the more evolved stellar population.
This indicates that the molecular gas may be ....
DR: ok, let's discuss this.

>>>>

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the C06 lens model (converted to
our cosmology) over the {\it HST} $I$-band image.
We note that the source plane half-light radius varies substantially with
wavelength: $R_e$ $\sim$\,4kpc and $\sim$7\,kpc based on models over
$V$-band \citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces recent massive \SF. The may be explained in part
due to the fact that $V$-band emission is
more susceptible to dust extinction than other bands.
The fact that the molecular gas (fuel for \SF) is more compact
than emission in the $I$ and $H$-bands,
which trace the more evolved stellar population, is consistent
with the picture that stars diffuse outward
after formation \citep{Calzetti01a}.
